---
title: "Codebook"
author: "AM"
date: "20/04/2021"
output: github_document
---

<!-- CodeBook.md is generated from CodeBook.Rmd. Please edit that file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      collapse = TRUE,
                      out.width = "100%"
                      )
```

# Codebook

## Original files

The following files available in the original data set were used as input:

- 'features_info.txt'

- 'features.txt'

- 'activity_labels.txt'

- 'train/X_train.txt'

- 'train/y_train.txt'

- 'test/X_test.txt'

- 'test/y_test.txt'

- 'train/subject_train.txt'

- 'test/subject_test.txt'

# Output files
"Output.txt" contains the following variables:

- Subject No.

- Activity

- Selected variables: mean and standard deviation for every available measurement, as described in "features_info.txt"

The values of each variable are the mean of the observations for each activity of each subject

The variable names are available in "variables.txt"
```{r var, echo=F}
read.table("variables.txt")

```
 
