---
title: "README"
author: "AM"
date: "20/04/2021"
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      collapse = TRUE,
                      out.width = "100%"
                      )
```

# Getting and Cleaning Data. Programming assignment

## Content

This repository contains the following files:

- "README.md": this file, which includes a description of the script

- "run_analysis.R": the full script

- "output.txt": a table exported by the run_analysis.R script, which includes the mean and standard deviation for each of the original measurements, averaged by subject and by activity.

- "variables.txt": the variable names for the output.txt file

- "CodeBook.md": the codebook explaining the new variables

## Script description

The script "run_analysis.R" downloads and unzips the dataset
```{r download}
#download and unzip the data files
url <- "https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"

download.file(url, "data.zip", method = "curl")
unzip("data.zip")

dir("UCI HAR Dataset/",recursive = T)
```

All relevant files are imported

```{r import}
# import all data files
test_data <- read.table("UCI HAR Dataset/test/X_test.txt")
test_labels <- read.table("UCI HAR Dataset/test/y_test.txt")
test_subject <- read.table("UCI HAR Dataset/test/subject_test.txt")

train_data <- read.table("UCI HAR Dataset/train/X_train.txt")
train_labels <- read.table("UCI HAR Dataset/train/y_train.txt")
train_subject <- read.table("UCI HAR Dataset/train/subject_train.txt")

activity_labels <- read.table("UCI HAR Dataset/activity_labels.txt")
features <- read.table("UCI HAR Dataset/features.txt")
```

The training set and test set are merged

```{r merge}
# combine training and test data sets
data <- rbind(train_data, test_data)
labels <- rbind(train_labels, test_labels)
subject <- rbind(train_subject, test_subject)
```

The column names in data (variables) are renamed based on the "features.txt" file.

```{r rename}
# rename columns with descriptive feature names (using "features.txt")
names(data) <- features$V2
names(labels) <- "activity"
names(subject) <- "subject"
```

"activity", is converted from number to factor, with descriptive name based on "activity_labels.txt"

```{r activity}
# change activity from number to factor with descriptive name
activity <- as.factor(activity_labels[match(labels$activity, activity_labels$V1),2])
```

"activity" and "subject" columns are added to the data set, generating a full data frame. Everything else is removed to clean the environment.

```{r full}
# merge all in one data set and remove everything else
full <- cbind(subject, activity, data)

rm(list = setdiff(ls(), "full"))
```

Finally, using dplyr, only mean and standard deviation are selected for each measurement, the average of each variable for each activity and each subject is calculated. the results are stored in a new dataset.
The output is written in a text file named "output.txt"
```{r dplyr}
# extract only measurements on mean and std, group and calculate mean
library(dplyr)
full <- as_tibble(full, .name_repair = "unique")
averaged <- full %>%
        select(subject:activity, contains(c("mean()", "std()"))) %>%
        group_by(subject, activity) %>%
        summarise(across(everything(), mean))

write.table(averaged, "output.txt", quote = F, row.names = F)
```

